Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-16 paper.tex
restructured
Added files via upload

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
\AP{the left panel of} Fig.~\ref{fig:Edens} we show that such a
distribution is not predicted by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. \CP{If CRps are predominantly
  advected with the cluster plasma, their distribution will be peaked
  towards the cluster center and shows a similar characteristics as
  the thermal plasma. As a consequence, the distribution of secondary
  electrons and the resulting radio synchrotron emission is also
  peaked since the hadronic reaction is a two-body scattering process
  (see Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls
  short of the observed extended and flat radio profile of the Coma
  cluster.}

\begin{figure*}
  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{Left: spatial distribution of CRp energy density in the
    Coma cluster. The red dash-dotted line shows the required
    distribution of seed CRps that generate secondary electrons via
    p-p collisions required to reproduce Coma radio brightness
    observations after Fermi-II reacceleration \citep{brunetti12}. The
    blue solid line shows the distribution of fossil CRps found in
    cosmological simulations, which disagrees with the required
    profile. \AP{To better compare the two models in this figure, we
      normalize the required distribution of CRps by fixing the total
      CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
      energy, consistent with observations
      \citep{2014ApJ...787...18A,2012ApJ...757..123A}. Right: the
      ratio of turbulent-to-thermal energy densities (solid lines) and
      cumulative energies (dotted lines) in our three models. The
      energy densities are parametrized as $\epsilon_\rmn{turb}
      \propto \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
      normalized such that the total turbulent energy in compressible
      modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
      total thermal energy $E_\rmn{th}$ inside the radio halo
      ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
      the uncertainty in the cluster turbulence and are motivated by
      the cosmological simulation in
      \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}}
  \label{fig:Edens}
\end{figure*}

Indeed, arriving at a seed population with the required
characteristics is highly constraining, and has the potential to teach
us much about the origin of CRps/CRes in clusters.  \CP{In this work,
  we use our hydrodynamical zoom simulations of galaxy clusters in a
  cosmological setting to follow the distribution functions of seed
  CRp and CRe population and integrate the Fokker-Planck equation of
  CR transport along Lagrangian particle trajectories. We resolve
  injection at structure formation shocks, account for various loss
  processes of CRs, and -- most importantly -- model second-order
  Fermi acceleration by CR interactions with magnetised
  turbulence. However, we assume a simplified and stationary model for
  magnetic fields and turbulence. We do not account for the
  time-varying energy density in compressible waves, which are thought
  to be necessary for the acceleration process
  \citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So
  our approach is orthogonal (and complementary) to e.g.,
  \citealp{2015ApJ...800...60M}. This enables us to vary parameters
  associated with the unknown continuation of magneto-hydrodynamical
  turbulence below the MHD scale and the overall amplitude of
  compressible waves.}

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work:
\AP{for details, see \citep[][ turbulent
    spectrum]{brunetti07,brunetti11}, \citep[][ injection scale of
    turbulens]{2015ApJ...800...60M}, \citep[][ energy density of
    turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
  for CR acceleration in shocks, \citep[][ in particular
    $K_{\rmn{ep}}$, acceleration efficiency]{pinzke13}, and for
  cosmological simulations, \citep[][ i.e., shock history, temperature
    profile, density profile, magnetic field profile]{pinzke10}.} All
these parameters are uncertain, and could potentially change our
predictions. We leave exploration of parameter space and the
interaction between free parameters to future work.

@@

The transport of relativistic electrons and protons in
the ICM is a complex process that depends both on the details of the
thermal component (gas density, temperature, and pressure) as well as
non-thermal component (turbulence, magnetic fields, fossil CRs). We
use high resolution galaxy cluster simulations to derive the thermal
and fossil CR properties (shock accelerated primary CRes and CRps, as
well as secondary CRes produced in p-p collisions)
\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}. In this
paper we focus on our simulated cluster, g72a, which is a massive
$1.6\times10^{15}\,M_\odot$ cluster that experienced a merger about
1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster mass,
density and temperature profiles are all similar to the well studied
Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will compare our
calculations to radio and gamma-ray observations of Coma.

\subsection{Acceleration}

\AP{We use a simple test-particle model for the CR acceleration and
  injection, where each shock inject CRs that trace a power-law in
  momentum,
  \begin{equation}
    f(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,
  \end{equation}
  determined by the normalization $C(t)$ and the spectral index
  $\alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}{(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}$
  that depends on the adiabatic index $\gamma_\rmn{ad} = 5/3$ and the
  Mach number of the shock $\mathcal{M}$. It is given by the ratio of
  the upstream velocity ($u_2$) and the sound speed ($c_s$). The CR
  number density and CR energy density are derived from $n_\rmn{CR} =
  \int_{p_\rmn{inj}}^\infty \dd p\, f(p)$ and $\epsilon_\rmn{CR} =
  \int_{p_\rmn{inj}}^\infty \dd p\, f(p) \,T(p)$, respectively, where
  $T(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
  particle with momentum $p$. We adopt a fit to Monte Carlo
  simulations of the thermal leakage process that relates the momentum
  of injected protons ($p_\rmn{inj}$) to the thermal energy
  ($p_\rmn{th}$) of the shocked plasma \citep{kang11}:
  \begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,k T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn th}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
  \end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which we will later see corresponds to a conservative maximum energy
acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_{\rmn inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see ][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{CR,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\epsilon_\rmn{CR,lin} =
  \eta_\rmn{CR,lin}(\mathcal{M})\,T_\rmn{CR}(\mathcal{M},p_\rmn{inj})\,n_\rmn{th}(T_2),
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\epsilon_\rmn{CR,lin}}{\Delta\epsilon_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\epsilon_\rmn{diss} = \epsilon_\rmn{th2} - \epsilon_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\epsilon_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.}

\AP{We limit the acceleration efficiency to $\zeta_{\rmn max}$ by
  steepening the spectral index of the injected population
  $\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_{\rmn lin}
  \leq \zeta_{\rmn max}$ is always fulfilled. The slope
  $\alpha_\rmn{inj}$ impact $\zeta_{\rmn inj}$ via the mean energy per
  particle given by $T_\rmn{CR} = \epsilon_\rmn{CR}/n_\rmn{CR}$. This
  procedure conserves energy and is motivated by models of non-linear
  shock acceleration where a sub-shock with a lower compression ratio
  (and hence steeper spectral index) forms
  \citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$,
  we find that for strong shocks where $\alpha \lesssim 2.3$ the
  spectral slope is steepened by a maximum of $\sim 10$ per cent in
  low temperature regimes ($kT\sim 0.1$~keV), while the steepening is
  much smaller for high temperature regimes ($kT\sim 10$~keV) that are
  more relevant for clusters. Since $p_{\rm inj}$ remains fixed, so
  does the CR number density $n_\rmn{CR}$. Hence we can solve for the
  renormalized normalization constant $C_\rmn{sub}$ using $n_\rmn{CR}$
  and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{CR,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$.} We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_{\rmn max} \sim 1-10\%$, depending on
the adopted model (for more details, see Section \ref{sec:results}).

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency (see \cite{pinzke13} for more
discussion). However, as recent PIC simulations have shown, this is
likely very different at weak shocks, with electrons efficiently
accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. \sout{In order not to violate energy conservation with a
  fixed limit for the acceleration efficiency, we steepen the spectral
  index of the accelerated CRps at the limit %\citep{pinzke13}
, which  mimics the non-linear CR modification of the shock
  %\citep{ellison00}
  . For weak shocks the efficiency is a factor 10-100
  lower and well below the limit.} Some observations of radio relics
suggest high values of $K_{\rmn{ep}}$, due to the absence of gamma-ray
emission, which probes the CRp population
\citep{2014MNRAS.437.2291V}. This suggests primary CRes as a viable
alternative scenario to secondary CRes as seeds for the giant RHs. In
our {\em M-primaries} scenario, the injected distribution of CRes is
derived in the same way as for the CRps. Once they have been
accelerated to relativistic energies, injected electrons and protons
are indistinguishable. We therefore assume that CRp and CRe have the
same distribution function $f_\rmn{CRe}(p) = K_\rmn{ep}
f_\rmn{CRp}(p)$, with a different normalization (due to differing
acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is viable for
  primarily perpendicular shocks][]{2014ApJ...794..153G}. While this
appears to contradict the radial bias of magnetic fields in the bulk
of the ICM as suggested by observations \citep{2010NatPh...6..520P}
and cluster simulations \citep{2011ApJ...740...81R}, it does not
necessarily apply to the accretion shock regions, which show a field
geometry with a net perpendicular bias with respect to the shock
normal---at least for giant radio relics \citep{2010Sci...330..347V}.

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses \AP{and the $\bnabla\bcdot
  \vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
  streaming. For details about $F_\rmn{stream}$ please see
  \citet{wiener13}.} During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that \AP{is thought to inject large
  turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
    also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
  about one Gyr after core passage the fields have decayed down to the
  smallest scales where reacceleration is most efficient ($D_{pp}\sim
  k_\rmn{cut}$) and the radio halo turns on shortly after. Note that
  the exact decay time of the turbulens is of minor importance, since
  the thermal and CR quantities are very similar a few 100 Myrs before
  and after $z=0$ where we have chosen to evaluate the simulations.}
\sout{injects large turbulent eddies. After about 1~Gyr those have
  decayed down to the scale needed to reaccelerate particles.} This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_D\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). \AP{This allows us to implicitly solve for CR streaming
  in our calculations, where we adopt a toy model that enforce a flat
  CRp profile at all quiescent times \citep{wiener13}. We assume that
  CRs cannot stream significantly past perpendicular $B$-fields at the
  accretion shock, so that the total number of CRs is conserved within
  the virial radius during the streaming process. Finally, since
  streaming is much more efficient for the CRps, we can ignore this
  effect for the CRes.}

@@

\AP{We focus on a scenario where the turbulence is injected at the
  largest scale that is driven by the merging cluster and accreting
  matter. The diffusion equation for isotropic MHD turbulence in
  $k$--space is given by}
\begin{eqnarray}
&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
=
{{\partial}\over{\partial k}}
\left[
k^2 D_{kk}
{{\partial}\over{\partial k}}
\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
\right]
- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
+ I(k,t)\nonumber\\
&
\label{modes_kinetic}
\end{eqnarray}
\AP{where we assume that the volumetric injection rate of turbulence
  $I(k,t)$ is constant over time with a fixed rate $I_0$ so that
  $I(k,t) \equiv I(k) = I_0\,\delta (k - k_o)$. The different damping
  terms are given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
  coefficient of magnetosonic waves in the $k$--space represented by
  \begin{equation}
    \label{eq:Dkk}
    D_{kk} \approx \Vph k^4
    \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
  \end{equation}
}

We adopt a simplified isotropic MHD turbulent spectrum \AP{based on
Kraichnan's picture} for the fast modes per elemental range $dk$ of
  the form

@@

for $k_0<k<k_\rmn{cut}$. \AP{Here we adopt an injection scale of the

@@

  \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}. \sout{At
    the same time we note that there is a large uncertainty in $k_0$,
    that is degenerate with the level of turbulence in compressible
    modes ($X_\rmn{tu}$) which is also highly uncertain. Increasing
    one of the parameters, allow us to decrease the other in order to
    keep $D_{pp}$ at the value needed to explain
    observations.}}\sout{, where we assume an injection scale for the
  turbulence, $k_0= 2\pi/(100~\mbox{kpc})$.} \AP{The profile of
  injected turbulence is also highly uncertain, however we assume it
  correlates to the thermal energy density to some power of the
  merging clusters. Hence we assume volumetric injection rate of

@@

  and determine the normalization by requiring that the turbulent
  energy in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k)
  \rmn{d}k \rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is
  the total thermal energy. We adopt a turbulent energy
  ratio\footnote{Simulations show that the compressible modes
    contribute a factor $0.2-0.4$ to the total turbulent energy

@@

    total turbulent energy is typically $10-30$\% of the thermal
    energy in a cluster which is in agreement with our adopted value
    of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo.} In
this work we investigate different spatial models for injected

@@

\epsilon_\rmn{th}^{\alpha_\rmn{tu}}/T^{1/4}$, where $T$ is the

@@

\AP{For reference we show in Table~\ref{tab:timescales} both the thermal
  quantities and the timescales for CR cooling and (re)acceleration
  for three different spatial regions of the RH. Interestingly the
  reacceleration timescale $\tau_D$ is very similar between our three
  models, where the difference comes from turbulent profile
  parameterized with $\alpha_\rmn{tu}$. This implies that even small
  differences in the turbulent profile could impact the seed CRs
  significantly.}

@@

% --- section: Results and discussion --- %

>>>>

However, there is a salient piece missing in the turbulent
reacceleration model. It relies heavily on the assumption of an
abundant, volume-filling population of seed suprathermal electrons;
direct Fermi II acceleration from the thermal pool is precluded by
strong Coulomb losses
\citep{2008ApJ...682..175P,2012ApJ...759..113C}. These seeds are
presumed to be either fossil CR electrons (CRes) accelerated by
diffusive shock acceleration (DSA) during structure formation
\citep{1999ApJ...520..529S}, or secondaries injected by hadronic
interaction of CR protons (CRps) with thermal protons
\citep{brunetti11}. While analytic estimates have been made, there has
been no ab initio demonstration that structure formation can lead to
the required abundance of seed electrons with the correct spatial and
spectral characteristics. This is a non-trivial requirement: Coulomb
cooling in dense cluster cores is severe, and DSA fossil electrons may
not survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
the left panel of Fig.~\ref{fig:Edens} we show that such a
distribution is not predicted by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
advected with the cluster plasma, their distribution will be peaked
towards the cluster center and shows a similar characteristics as the
thermal plasma. As a consequence, the distribution of secondary
electrons and the resulting radio synchrotron emission is also peaked
since the hadronic reaction is a two-body scattering process (see
Fig.~Fig.~\ref{fig:Edens}). Hence, the simulated emission falls short
of the observed extended and flat radio profile of the Coma cluster.

\begin{figure*}
  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \caption{Spatial distribution of CRp energy density in the Coma
    cluster. The red dash-dotted line shows the required distribution
    of seed CRps that generate secondary electrons via p-p collisions
    required to reproduce Coma radio brightness observations after
    Fermi-II reacceleration \citep{brunetti12}. The blue solid line
    shows the distribution of fossil CRps found in cosmological
    simulations, which disagrees with the required profile. To better
    compare the two models in this figure, we normalize the required
    distribution of CRps by fixing the total CRp energy $E_\rmn{CR}$
    to 0.3 percent of the total thermal energy, consistent with
    observations \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
  \label{fig:Edens}
\end{figure*}

Indeed, arriving at a seed population with the required
characteristics is highly constraining, and has the potential to teach
us much about the origin of CRps/CRes in clusters.  In this work, we
use our hydrodynamical zoom simulations of galaxy clusters in a
cosmological setting to follow the distribution functions of seed CRp
and CRe population and integrate the Fokker-Planck equation of CR
transport along Lagrangian particle trajectories. We resolve injection
at structure formation shocks, account for various loss processes of
CRs, and -- most importantly -- model second-order Fermi acceleration
by CR interactions with magnetised turbulence. However, we assume a
simplified and stationary model for magnetic fields and turbulence. We
do not account for the time-varying energy density in compressible
waves, which are thought to be necessary for the acceleration process
\citep{brunetti07,brunetti11}, as the cluster merger proceeds.  So our
approach is orthogonal (and complementary) to e.g.,
\citealp{2015ApJ...800...60M}. This enables us to vary parameters
associated with the unknown continuation of magneto-hydrodynamical
turbulence below the MHD scale and the overall amplitude of
compressible waves.

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work: for
details, see \citep[][ turbulent spectrum]{brunetti07,brunetti11},
\citep[][ injection scale of turbulens]{2015ApJ...800...60M},
\citep[][ energy density of
  turbulence]{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks, \citep[][ in particular $K_{\rmn{ep}}$,
  acceleration efficiency]{pinzke13}, and for cosmological
simulations, \citep[][ i.e., shock history, temperature profile,
  density profile, magnetic field profile]{pinzke10}. All these
parameters are uncertain, and could potentially change our
predictions. We leave exploration of parameter space and the
interaction between free parameters to future work.

@@

The transport of relativistic electrons and protons in
the ICM is a complex process that depends both on the details of the
thermal component (gas density, temperature, and pressure) as well as
non-thermal component (turbulence, magnetic fields, fossil CRs). We
use high resolution galaxy cluster simulations to derive the thermal
and fossil CR properties (shock accelerated primary CRes and CRps, as
well as secondary CRes produced in p-p collisions)
\citep{2007MNRAS.378..385P,pfrommer08,pinzke10,pinzke13}.

[explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$]

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
- \bnabla\bcdot \vec{F}_\rmn{stream}
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses and the $\bnabla\bcdot
\vec{F}_\rmn{stream}$ terms represent super-Alfv{\'e}nic CR
streaming. For details about $F_\rmn{stream}$ please see
\citet{wiener13}. During post-processing of our Coma-like cluster
simulation, we solve the Fokker-Planck equation over a redshift
interval from $z=5$ to 0. The simulated cluster undergoes a major
merger over the last 1-2~Gyrs that is thought to inject large
turbulent eddies. Following \citet{brunetti07,brunetti11} \citep[see
  also][]{2004ApJ...614..757Y,2015ApJ...800...60M} we assume that
about one Gyr after core passage the fields have decayed down to the
smallest scales where reacceleration is most efficient ($D_{pp}\sim
k_\rmn{cut}$) and the radio halo turns on shortly after. Note that the
exact decay time of the turbulens is of minor importance, since the
thermal and CR quantities are very similar a few 100 Myrs before and
after $z=0$ where we have chosen to evaluate the simulations. This
delay naturally explains why giant radio halos are only seen in a
fraction of all merging clusters. In all our calculations we assume
that turbulent reacceleration efficiently accelerates particles for
$\tau_\rmn{cl}\sim650$~Myrs (which is roughly the cascade time on which
turbulence is damped) and that during this turbulent phase CR
streaming and spatial diffusion can be neglected. In our \Mstream
model, CR streaming and diffusion are incorporated separately during
kinematically quiescent times that precede the merger. As a result,
flat CRp profiles are produced on relatively short timescales ($\sim
0.1-0.5$ Gyr). This allows us to implicitly solve for CR streaming in
our calculations, where we adopt a toy model that enforce a flat CRp
profile at all quiescent times \citep{wiener13}. We assume that CRs
cannot stream significantly past perpendicular $B$-fields at the
accretion shock, so that the total number of CRs is conserved within
the virial radius during the streaming process. Finally, since
streaming is much more efficient for the CRps, we can ignore this
effect for the CRes.

@@

We focus on a scenario where the turbulence is injected at the largest
scale that is driven by the merging cluster and accreting matter. The
diffusion equation for isotropic MHD turbulence in $k$--space is given
by
\begin{eqnarray}
&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
=
{{\partial}\over{\partial k}}
\left[
k^2 D_{kk}
{{\partial}\over{\partial k}}
\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
\right]
- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
+ I(k,t)\nonumber\\
&
\label{modes_kinetic}
\end{eqnarray}
where we assume that the volumetric injection rate of turbulence
$I(k,t)$ is constant over time with a fixed rate $I_0$ so that $I(k,t)
\equiv I(k) = I_0\,\delta (k - k_o)$. The different damping terms are
given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
coefficient of magnetosonic waves in the $k$--space represented by
\begin{equation}
  \label{eq:Dkk}
  D_{kk} \approx \Vph k^4
  \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
\end{equation}

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form

@@

for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the

@@

\citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
The profile of injected turbulence is also highly uncertain, however
we assume it correlates to the thermal energy density to some power of
the merging clusters. Hence we assume volumetric injection rate of

@@

and determine the normalization by requiring that the turbulent energy
in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k
\rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total
thermal energy. We adopt a turbulent energy ratio\footnote{Simulations
  show that the compressible modes contribute a factor $0.2-0.4$ to
  the total turbulent energy

@@

  total turbulent energy is typically $10-30$\% of the thermal energy
  in a cluster which is in agreement with our adopted value of
  $X_\rmn{tu}$.}  $X_\rmn{tu}=0.06$ within the radio halo. In this
work we investigate different spatial models for injected

@@

\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the

@@

\begin{figure*}
  \includegraphics[width=1.0\columnwidth]{turb_profile_ratio_tot.eps}
  \caption{The ratio of turbulent-to-thermal energy densities (solid
    lines) and cumulative energies (dotted lines) in our three
    models. The energy densities are parametrized as
    $\epsilon_\rmn{turb} \propto
    \epsilon_\rmn{th}^{(\alpha_{\rmn{tu}}+1)/2}/T^{1/4}$ and
    normalized such that the total turbulent energy in compressible
    modes $E_\rmn{turb}$ for each scenario makes up about 6\% of the
    total thermal energy $E_\rmn{th}$ inside the radio halo
    ($R_\rmn{RH}\approx0.6R_{200}$). The turbulent profiles explore
    the uncertainty in the cluster turbulence and are motivated by the
    cosmological simulation in
    \citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V}.}
  \label{fig:Edens}
\end{figure*}

For reference we show in Table~\ref{tab:timescales} both the thermal
quantities and the timescales for CR cooling and (re)acceleration for
three different spatial regions of the RH. Interestingly the
reacceleration timescale $\tau_D$ is very similar between our three
models, where the difference comes from turbulent profile
parameterized with $\alpha_\rmn{tu}$. This implies that even small
differences in the turbulent profile could impact the seed CRs
significantly.

@@

\subsection{Spherically symmetric models}

[Anders, your analytical methodology should go here]

\subsection{Cosmological simulation methodology}

In this
paper we focus on our simulated cluster, g72a, which is a massive
$1.6\times10^{15}\,M_\odot$ cluster that experienced a merger about
1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster mass,
density and temperature profiles are all similar to the well studied
Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will compare our
calculations to radio and gamma-ray observations of Coma.
